\LARGE \bf Mean Estimation from One-Bit Measurements

### 2021-09-29 proof-sgd.tex
fixed all comments after first revision, sending to John

The estimation algorithm~\eqref{eq:sgd_alg} is a special
case of the stochastic gradient procedures in the papers
\cite{PolyakJu92, polyak1990new}.
We rely on several of their results. Throughout this proof,
we assume without loss of generality that the median
$\theta = \mbox{med}(P) = 0$.

@@

Consider the following simplified version of
\cite[Thm. 4]{polyak1992acceleration}:
\begin{corollary}{\cite[Thms. 3 \& 4]{PolyakJu92}}
  \label{corollary:polyak-juditsky}
  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ random
  variables, and
  \begin{equation*}
  X_i = \theta + Z_i.
  \end{equation*}
  Define
  \begin{align}
    \begin{split}
      \theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
      \bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
    \end{split}
    \label{eq:Polyak_Juditsky_alg}
  \end{align}
  where in addition,
  \begin{enumerate}[(i)]
  \item There exists $K_1$ such that $\left| \varphi(x) \right| \leq
    K_1(1+|x|)$ for all $x\in \R$.
  \item The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
  \item \label{item:zero-gradient}
    The function $\psi(x) \defeq \ex{ \varphi(x+Z_1)}$
    satisfies $\psi(0) = 0$ and
    $x\psi(x) > 0$ for $x\neq 0$.  Moreover, $\psi$ is differentiable
    at 0 with $\psi'(0) > 0$ and there exists
    $K_2$ and $0 < \lambda \leq 1$ such that
    \begin{equation}
      \label{eqn:local-hessian-psi}
        \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}
    \end{equation}
    \newtext{for all $|x|<r$ for some $r>0$ small enough. }
  \item The function 
    $\chi(x) \defeq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
  \end{enumerate}
  Then $\bar{\theta}_n \cas \theta$ and $ \sqrt{n}({\theta}_n - \theta)
  \cd \normal(0,V)$ for
  $V = \frac{ \chi(0)} {\psi'(0)^2}$.
\end{corollary}

@@

By the assumption in Theorem~\ref{thm:sgd} that the density $f$
is Lipschitz continuous, \newtext{$\sqrt{f}$ is Lipschitz continuous hence absolutely continuous}. We see that the location family
$\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
satisfies the conditions of Lemma~\ref{lemma:qmd}.

It remains to show that the average $\bar{\theta}_n$ is regular \newtext{at $\theta$ with the limiting distribution $\Ncal(0,(4f(0)^2)^{-1})$}:
\begin{lemma}
  \label{lemma:sgd-median-regular}
  Let $h_n \to h \in \R$, and define $P_n = P_{\theta + h_n / \sqrt{n}}^n$.
  Then 
  \begin{align}
    \label{eqn:sgd-median-regular}
    \newtext{
    \sqrt{n}\left( \bar{\theta}_n - \theta \right)
    \mathop{\cd}_{P_n}
    \normal\left( h,\frac{1}{4 f(0)^2}\right).
    }
  \end{align}
\end{lemma}
\begin{proof}
  To show the convergence~\eqref{eqn:sgd-median-regular} we use the
  following refinement of Corollary~\ref{corollary:polyak-juditsky}, which
  provides a generalized convergence result for iteratively defined
  $\theta_n$, and whose
  proof we defer to Section~\ref{proof:normal-expansion}.
  %
  \begin{corollary}
    \label{corollary:normal-expansion}
    Let the conditions of Corollary~\ref{corollary:polyak-juditsky} hold,
    meaning that $\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i -
    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $\{Z_i\}$ are i.i.d.\ with
    $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
    condition that there exist $0 < \lambda \le 1$ and $K < \infty$ such
    that
    \begin{equation}
      \label{eqn:additional-local-smooth}
      \E[|\varphi(x + Z_1) - \varphi(Z)|^2]
      \le K (|x|^\lambda + x^2).
    \end{equation}
    Set $\Delta_i \defeq \theta_i - \theta$ and $\bar{\Delta}_n \defeq \frac{1}{n}
    \sum_{i=1}^n \Delta_i$. Then
    \begin{enumerate}[(i)]
    \item \label{item:regularity}
      The sequence $\{\Delta_i\}$ is regular, that is,
      \begin{equation}
        \sqrt{n} \bar{\Delta}_n
        = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)
        + o_{P,n}(1).
        \label{eq:normal_expansion_lem}
      \end{equation}
    \item \label{item:apply-le-cam} Let $\{Z_i\}$ as in
      Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
      density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
        - h)}$, and assume that $I_h \defeq \E_p[\score_h(Z_1)^2]$ is
      continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
      \begin{equation*}
        \sqrt{n} \bar{\Delta}_n
        \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z_1) \score_0(Z_1)],
        \frac{\chi(0)}{\psi'^2(0)} \right).
      \end{equation*}
    \end{enumerate}
  \end{corollary}

@@

\newtext{Fix $\theta \in \R$}. Apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
$\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
The update~\eqref{eq:polyak_new_measurements} gives
\begin{align*} 
  U_n %% & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
  & = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
\end{align*}
so the estimator $\bar{U}_n$ is identical to the stochastic gradient
estimator~\eqref{eq:sgd_alg} with $\bar{\theta}_n = \frac{1}{n} \sum_{i =
  1}^n \theta_i$. We have $\E[\varphi(x + Z)^4] = 1$ and by assumption the
Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the functions $\psi$
and $\chi$ have the desired conditions of
Corollary~\ref{corollary:polyak-juditsky} (as we verify in
Section~\ref{sec:proof-normal-sgd}). Finally, the function $\theta \mapsto
\E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
that for $x^\star = \theta$ and $g'' \defeq 1$, \newtext{we may apply
Corollary~\ref{corollary:polyak-mse} to obtain}
\begin{align*}
\ex{(\bar{\theta}_n - \theta)^2} = \frac{1}{4nf(0)^2} + o(n^{-1}).
\end{align*}
\newtext{
From here, existence of the second moment of $\pi$ implies \eqref{eq:thm:sgd_3}. }
%Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.}

@@

The proof of part~\eqref{item:regularity} requires two additional lemmas of
Polyak and Juditsky~\cite{PolyakJu92}.
\begin{lem}[\cite{PolyakJu92}, Lemma 2]
  \label{lemma:polyak-expansion}
  Define the process $\Delta_i^1 = \Delta_{i-1}^1
  - \gamma_i (A \Delta_{i-1}^1 + \xi_i)$ for $i = 1, 2, \ldots$.
  Assume that $A>0$ and the stepsizes $\gamma_i$ satisfy
  condition~\eqref{eqn:lazy-gamma}. Then
  for $\bar{\Delta}_n^1 = \frac{1}{n} \sum_{i = 1}^n \Delta_i^1$, we have
  \begin{equation}
    \label{eqn:polyak-expansion}
    \sqrt{n} \bar{\Delta}_n^1
    % = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1
    = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}
    + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i
    + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
  \end{equation}
  where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq
  K$ and $|w_i^n|\leq K$ for some $K< \infty$, and $\lim_{n\to \infty}
  \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0$.
\end{lem}

\begin{lem}[\cite{PolyakJu92}]
  \label{lemma:converging-power-sum}
  Under the conditions of Corollary~\ref{corollary:normal-expansion},
  with probability 1,
  \begin{equation*}
  \sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty.
  \end{equation*}
\end{lem}
\noindent
Lemma~\ref{lemma:converging-power-sum} follows from the proof of Theorem 2
in \cite[page 851]{polyak1992acceleration}.

We separate the proof of part~\eqref{item:regularity} into two lemmas, which
mirror the proofs of Polyak and Juditsky~\cite{PolyakJu92}; together they
immediately give the result.

@@

  The term \eqref{eq:PJ_proof2} is somewhat more challenging to control.
  We define
  \begin{equation*}
    \epsilon_i \defeq \psi(\Delta_{i-1}) + \varphi(Z_i)
    - \varphi(\Delta_{i-1}+Z_i),
  \end{equation*}
  and let
  $\mc{F}_i = \sigma(Z_1, \ldots, Z_i)$ be the $\sigma$-field of the randomness
  through time $i$. We use a square integrable martingale convergence
  theorem~\cite[Exercise~5.3.35]{Dembo16}. Noting that
  $\Delta_i \in \mc{F}_i$, we have
  \begin{align}
    \E[\epsilon_i^2 \mid \mc{F}_{i-1}]
    & = \E[(\psi(\Delta_{i-1}) + \varphi(Z_i)
      - \varphi(\Delta_{i-1} + Z_i))^2 \mid \mc{F}_{i-1}]
    \nonumber \\
    & \le 2 \psi(\Delta_{i-1})^2
    + 2 \E[(\varphi(\Delta_{i-1} + Z_i) - \varphi(Z_i))^2 \mid \mc{F}_{i-1}]
    \nonumber \\
    & \le
    K \left[|\Delta_{i-1}|^{1 + \lambda}
      + |\Delta_{i-1}|^\lambda
      + \Delta_{i-1}^2 \right],
    \label{eqn:bound-psi-error-expectations}
  \end{align}
  where inequality~\eqref{eqn:bound-psi-error-expectations} follows by the
  conditions~\eqref{eqn:local-hessian-psi}
  and~\eqref{eqn:additional-local-smooth}, and $\E[\varepsilon_i \mid
    \mc{F}_{i-1}] = 0$ for all $i$ by definition of $\psi(x) = \E[\varphi(x
    + Z)]$ and that $\psi(0) = 0$.  We now control the expectations of these
  quantities. For $R < \infty$, define the stopping time $\tau_R \defeq \inf
  \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
  for each $i$.  Then using~\cite[Eq.~(A14)]{PolyakJu92}, we have
  \begin{equation*}
    \E[\Delta_i^2 \indic{\tau_R > i}] \le K \gamma_i,
  \end{equation*}
  and so inequality~\eqref{eqn:bound-psi-error-expectations} gives that
  \begin{equation*}
    \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
      |\varepsilon_i|^2 \indic{\tau_R > i} \bigg]
    \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
    < \infty
    ~~ \mbox{so} ~~
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2 \indic{\tau_R > i} < \infty
    ~ \mbox{a.s.}
  \end{equation*}
  by Condition~\eqref{eqn:lazy-gamma}. \newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s. bounded, with probability 1 there exists some (random) $R < \infty$ such that $\tau_R = \infty$.} We obtain that 
  \begin{equation*}
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2  < \infty
    ~ \mbox{a.s.}.
  \end{equation*}
  Applying the square integrable martingale convergence
  theorem of \cite[Ex.~5.3.35]{Dembo16}, we have
  \begin{equation*}
    \frac{1}{\sqrt{n}} \sum_{i = 1}^n
    \left(\frac{1}{\psi'(0)} + w_i^n\right) \epsilon_i \cas 0,
  \end{equation*}
  so that both equations~\eqref{eq:PJ_proof1} and~\eqref{eq:PJ_proof2}
  converge almost surely to 0.
\end{proof}

>>>>

The estimation algorithm~\eqref{eq:sgd_alg} is a special
case of the stochastic gradient procedures in the papers
\cite{polyak1992acceleration, polyak1990new}.
We rely on several of their results. Throughout this proof,
we assume without loss of generality that the median
$\theta = \mbox{med}(P) = 0$.

@@

Consider the following simplified version of
\cite[Thm. 4]{polyak1992acceleration}:
\begin{corollary}{\cite[Thms. 3 \& 4]{polyak1992acceleration}}
  \label{corollary:polyak-juditsky}
  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ \newtext{zero-mean} random
  variables, and
  \begin{equation*}
  X_i = \theta + Z_i.
  \end{equation*}
  Define
  \begin{align}
    \begin{split}
      \theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
      \bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
    \end{split}
    \label{eq:Polyak_Juditsky_alg}
  \end{align}
  where in addition,
  \begin{enumerate}[(i)]
  \item There exists $K_1$ such that $\left| \varphi(x) \right| \leq
    K_1(1+|x|)$ for all $x\in \R$.
  \item The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
  \item \label{item:zero-gradient}
    The function $\psi(x) \defeq \ex{ \varphi(x+Z_1)}$
    satisfies $\psi(0) = 0$ and
    $x\psi(x) > 0$ for $x\neq 0$. Moreover, $\psi$ is differentiable
    at 0 with $\psi'(0) > 0$ and there exists
    $K_2$, $0 < \lambda \leq 1$, \newtext{and $r>0$}, such that
    \begin{equation}
      \label{eqn:local-hessian-psi}
        \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}
    \end{equation}
    \newtext{for all $|x|<r$. }
  \item The function 
    $\chi(x) \defeq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
  \end{enumerate}
  Then $\bar{\theta}_n \cas \theta$ and $ \sqrt{n}({\theta}_n - \theta)
  \cd \normal(0,V)$ for
  $V = \frac{ \chi(0)} {\psi'(0)^2}$.
\end{corollary}

@@

By the assumption in Theorem~\ref{thm:sgd} that the density $f$
is Lipschitz continuous, \newtext{$f$ is absolutely continuous hence 
$\sqrt{f}$ is absolutely continuous}. We see that the location family
$\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
satisfies the conditions of Lemma~\ref{lemma:qmd}.

It remains to show that the average $\bar{\theta}_n$ is regular \newtext{at $\theta$ with the limiting distribution $\Ncal(0,(4f(0)^2)^{-1})$}:
\begin{lemma}
  \label{lemma:sgd-median-regular}
  Let $h_n \to h \in \R$, and define $P_{n,h} = P_{\theta + h_n / \sqrt{n}}^n$.
  Then 
  \begin{align}
    \label{eqn:sgd-median-regular}
    \newtext{
    \sqrt{n}\left( \bar{\theta}_n - \theta \right)
    \mathop{\cd}_{P_{n,h}}
    \normal\left( h,\frac{1}{4 f(0)^2}\right).
    }
  \end{align}
\end{lemma}
\begin{proof}
  To show the convergence~\eqref{eqn:sgd-median-regular} we use the
  following refinement of Corollary~\ref{corollary:polyak-juditsky}, which
  provides a generalized convergence result for iteratively defined
  $\theta_n$, and whose
  proof we defer to Section~\ref{proof:normal-expansion}.
  %
  \begin{corollary}
    \label{corollary:normal-expansion}
    Let the conditions of Corollary~\ref{corollary:polyak-juditsky} hold,
    meaning that $\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i -
    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $\{Z_i\}$ are i.i.d.\ with
    $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
    condition that there exist $0 < \lambda \le 1$ and $K < \infty$ such
    that
    \begin{equation}
      \label{eqn:additional-local-smooth}
      \E[|\varphi(x + Z_1) - \varphi(Z)|^2]
      \le K (|x|^\lambda + x^2).
    \end{equation}
    Set $\Delta_i \defeq \theta_i - \theta$ and $\bar{\Delta}_n \defeq \frac{1}{n}
    \sum_{i=1}^n \Delta_i$. Then
    \begin{enumerate}[(i)]
    \item \label{item:regularity}
      The sequence $\{\Delta_i\}$ is regular, that is,
      \begin{equation}
        \sqrt{n} \bar{\Delta}_n
        = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)
        + o_{P,n}(1).
        \label{eq:normal_expansion_lem}
      \end{equation}
    \item \label{item:apply-le-cam} Let $\{Z_i\}$ as in
      Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
      density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
        - h)}$, and assume that $I_h \defeq \E_p[\score_h(Z_1)^2]$ is
      continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
      \begin{equation*}
        \sqrt{n} \bar{\Delta}_n
        \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z_1) \score_0(Z_1)],
        \frac{\chi(0)}{\psi'^2(0)} \right).
      \end{equation*}
    \end{enumerate}
  \end{corollary}

@@

\newtext{Fix $\theta \in \R$}. Apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
$\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
The update~\eqref{eq:polyak_new_measurements} gives
\begin{align*} 
  U_n %% & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
  & = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
\end{align*}
so the estimator $\bar{U}_n$ is identical to the stochastic gradient
estimator~\eqref{eq:sgd_alg} with $\bar{\theta}_n = \frac{1}{n} \sum_{i =
  1}^n \theta_i$. We have $\E[\varphi(x + Z)^4] = 1$ and by assumption the
Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the functions $\psi$
and $\chi$ have the desired conditions of
Corollary~\ref{corollary:polyak-juditsky} (as we verify in
Section~\ref{sec:proof-normal-sgd}). Finally, the function $\theta \mapsto
\E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
that for $x^\star = \theta$ and $g'' \defeq 1$, \newtext{we may apply
Corollary~\ref{corollary:polyak-mse} to obtain}
\begin{align*}
\ex{(\bar{\theta}_n - \theta)^2} = \frac{1}{4nf(0)^2} + o(n^{-1}).
\end{align*}
\newtext{
From here, existence of the second moment of $\pi$ implies \eqref{eq:adaptive_3}.}
%Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.}

@@

The proof of part~\eqref{item:regularity} requires two additional lemmas of
Polyak and Juditsky~\cite{polyak1992acceleration}.
\begin{lem}[\cite{polyak1992acceleration}, Lemma 2]
  \label{lemma:polyak-expansion}
  Define the process $\Delta_i^1 = \Delta_{i-1}^1
  - \gamma_i (A \Delta_{i-1}^1 + \xi_i)$ for $i = 1, 2, \ldots$.
  Assume that $A>0$ and the stepsizes $\gamma_i$ satisfy
  condition~\eqref{eqn:lazy-gamma}. Then
  for $\bar{\Delta}_n^1 = \frac{1}{n} \sum_{i = 1}^n \Delta_i^1$, we have
  \begin{equation}
    \label{eqn:polyak-expansion}
    \sqrt{n} \bar{\Delta}_n^1
    % = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1
    = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}
    + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i
    + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
  \end{equation}
  where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq
  K$ and $|w_i^n|\leq K$ for some $K< \infty$, and $\lim_{n\to \infty}
  \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0$.
\end{lem}

\begin{lem}[\cite{polyak1992acceleration}]
  \label{lemma:converging-power-sum}
  Under the conditions of Corollary~\ref{corollary:normal-expansion},
  with probability 1,
  \begin{equation*}
  \sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty.
  \end{equation*}
\end{lem}
\noindent
Lemma~\ref{lemma:converging-power-sum} follows from the proof of Theorem 2
in \cite[page 851]{polyak1992acceleration}.

We separate the proof of part~\eqref{item:regularity} into two lemmas, which
mirror the proofs of Polyak and Juditsky~\cite{polyak1992acceleration}; together they
immediately give the result.

@@

  The term \eqref{eq:PJ_proof2} is somewhat more challenging to control.
  We define
  \begin{equation*}
    \epsilon_i \defeq \psi(\Delta_{i-1}) + \varphi(Z_i)
    - \varphi(\Delta_{i-1}+Z_i),
  \end{equation*}
  and let
  $\mc{F}_i = \sigma(Z_1, \ldots, Z_i)$ be the $\sigma$-field of the randomness
  through time $i$. We use a square integrable martingale convergence
  theorem~\cite[Exercise~5.3.35]{Dembo16}. Noting that
  $\Delta_i \in \mc{F}_i$, we have
  \begin{align}
    \E[\epsilon_i^2 \mid \mc{F}_{i-1}]
    & = \E[(\psi(\Delta_{i-1}) + \varphi(Z_i)
      - \varphi(\Delta_{i-1} + Z_i))^2 \mid \mc{F}_{i-1}]
    \nonumber \\
    & \le 2 \psi(\Delta_{i-1})^2
    + 2 \E[(\varphi(\Delta_{i-1} + Z_i) - \varphi(Z_i))^2 \mid \mc{F}_{i-1}]
    \nonumber \\
    & \le
    K \left[|\Delta_{i-1}|^{1 + \lambda}
      + |\Delta_{i-1}|^\lambda
      + \Delta_{i-1}^2 \right],
    \label{eqn:bound-psi-error-expectations}
  \end{align}
  where inequality~\eqref{eqn:bound-psi-error-expectations} follows by the
  conditions~\eqref{eqn:local-hessian-psi}
  and~\eqref{eqn:additional-local-smooth}, and $\E[\varepsilon_i \mid
    \mc{F}_{i-1}] = 0$ for all $i$ by definition of $\psi(x) = \E[\varphi(x
    + Z)]$ and that $\psi(0) = 0$.  We now control the expectations of these
  quantities. 
  \newtext{
  As in the proof of Theorems~2 and~4 in \cite{polyak1992acceleration}, the Robbins-Siegmund Theorem \cite{robbins1971convergence} applies to the increment of $|\Delta_t|^2$ implies that for every 
  $\epsilon>0$ there exists some $R>0$ such that
  \begin{align}
  \label{eq:sup_delta}
  \Prob\left(\sup_i |\Delta_i| \le R \right) \ge 1-\epsilon.
  \end{align} 
  Define the the stopping time $\tau_R \defeq \inf
  \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
  for each $i$. 
  }
  Then using~\cite[Eq.~(A14)]{polyak1992acceleration}, we have
  \begin{equation*}
    \E[\Delta_i^2 \indic{\tau_R > i}] \le K \gamma_i,
  \end{equation*}
  and so inequality~\eqref{eqn:bound-psi-error-expectations} gives that
  \begin{equation*}
    \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
      |\varepsilon_i|^2 \indic{\tau_R > i} \bigg]
    \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
    < \infty
    ~~ \mbox{so} ~~
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2 \indic{\tau_R > i} < \infty
    ~ \mbox{a.s.}
  \end{equation*}
  by Condition~\eqref{eqn:lazy-gamma}. Since
  \begin{align*}
\left\{ \sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}} < \infty \subset \left\{ \sup_i |\Delta_i| \leq R \right\} \cap \left\{ \sum_{i=0}^\infty  \right\}
 \right\},
  \end{align*}
  \newtext{it follows from \eqref{eq:sup_delta} and by the arbitrary choice of $\epsilon$ that}
  %\newtext{As it follows from \cite[Eq.~(A11)]{polyak1992acceleration} that $\Prob\left( \sup |\Delta_t| < \infty  \right)=1$}, we obtain
  %\newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s. bounded, with probability 1 there exists some (random) $R < \infty$ such that $\tau_R = \infty$.} We obtain that 
  \begin{equation*}
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2  < \infty
    ~ \mbox{a.s.}.
  \end{equation*}
  Applying the square integrable martingale convergence
  theorem of \cite[Ex.~5.3.35]{Dembo16}, we have
  \begin{equation*}
    \frac{1}{\sqrt{n}} \sum_{i = 1}^n
    \left(\frac{1}{\psi'(0)} + w_i^n\right) \epsilon_i \cas 0,
  \end{equation*}
  so that both equations~\eqref{eq:PJ_proof1} and~\eqref{eq:PJ_proof2}
  converge almost surely to 0.
\end{proof}
